We are not the 99 percent: quantifying bright satellite distributions in the Local Group

### 2017-11-03 paper/paper.tex
some pagragraphs

The presence of a Vast Polar Structure of satellites around the Milky
Way has been stablished in the last decade.
The question whether this configuration is atypical in the observable
universe cannot be proberly addressed given the current limits in
observations. 
So far it has only been possible to contraint that $5\%$ of the
Milky-Way like galaxies in the Universe have two bright satellite
galaxies as is the case of the Milky Way and its Large and Small
Magellanic Clouds.

The closest system that could help us in providing a baseline for
comparison is the Andromeda galaxy, M31. 
Its close enough that an observational

This has prompted a discussion on whether the current dominant
paradigm for galaxy formation based on a Cold Dark Matter cosmology in
a expanding universe described by General Relativity with a
Cosmological Constant, so-called Lambda Cold Dark Matter (LCDM) model
can account for the existence of such a structure.

>>>>

The presence of a Vast Polar Structure of satellites around the Milky
Way has been stablished in the last decade.
This structure can be easily described by global quantities of the
brightest

The question whether this configuration is atypical in the observable
universe cannot be proberly addressed given the current limits in
observations. 
So far it has only been possible to contraint that $5\%$ of the
Milky-Way like galaxies in the Universe have two bright satellite
galaxies as is the case of the Milky Way and its Large and Small
Magellanic Clouds.

The closest system that could help us in providing a baseline for
comparison is the Andromeda galaxy, M31. 
Its close enough that an observational study of its satellite
population is possible, with the great advantage of having a
perpective from a distance and not from within, as is the case for our
Galaxy. 
These studies also found a planar satellite
distributions.
This time not in the whole distribution, but in a subset of $15$
satellites out of an homogeneous sample of $27$ satellites.

This has prompted a discussion on whether this satellite distributions
are easily found in structure formation simulations done in the
current dominant paradigm for galaxy formation.
This paradigm, based on a Cold Dark Matter cosmology in
a expanding universe described by General Relativity with a
Cosmological Constant, is the so-called Lambda Cold Dark Matter
(LCDM).

The consensus is that these structures are hard to find in
simulations. 
Some studies have focused on the study of individual dark matter halos
that could host galaxies like the MW or M31, while some other studies
have tried to simulate the formation of galaxy pairs resembling both
the MW and M31.
The transition from studying individual halos to pairs has been
motivated by the realization that
